---
title: Cubic SVM
output:
  html_document: 
    toc: yes
  pdf_document: default
---

## Load Dataset

```{r}
X <- read.csv("./data/X_.csv", header = TRUE)
y <- read.csv("./data/y_.csv", header = TRUE)
```

## Dataset Division

```{r}
data <- cbind(X, y)

# set.seed(123) # 123
indices <- 1:nrow(data)
shuffled_indices <- sample(indices)
train_size <- floor(0.7 * length(indices)) # 修改比例
train_indices <- shuffled_indices[1:train_size]
test_indices <- shuffled_indices[(train_size + 1):length(indices)]

train_data <- data[train_indices, ]
test_data <- data[test_indices, ]

```

## Cubic SVM

```{r}
# Load the e1071 library
library(e1071)

# Train a Cubic SVM model
cubic_svm_model <- svm(dod ~ ., data = train_data, kernel = "polynomial", degree = 3)

# Make predictions using the trained models
predictions <- predict(cubic_svm_model, newdata = test_data)

```

## Performance

```{r}
confusion_matrix <- table(as.numeric(test_y), as.numeric(ifelse(predictions > 0.5, 1, 0)))

## 计算 Accuracy
accuracy <- sum(diag(confusion_matrix)) / sum(confusion_matrix)
cat("Accuracy:", accuracy, "\n")

## 计算 Recall
recall <- diag(confusion_matrix)[1] / sum(confusion_matrix[1,])
cat("Recall:", recall, "\n")

## 计算 F1 Score
precision <- diag(confusion_matrix)[1] / colSums(confusion_matrix)[1]
f1_score <- 2 * (precision * recall) / (precision + recall)
cat("F1 Score:", f1_score, "\n")

```

# ROC Curve

```{r}
library(pROC)
roc_obj <- roc(as.numeric(test_y), 
               as.numeric(predictions),)

plot(
  roc_obj,
  col = "red", 
  main = "ROC Curve - Cubic SVM",
  legacy.axes = T, # y轴格式更改
  print.auc = TRUE, # 显示AUC面积
  print.thres = TRUE, # 添加截点和95%CI
  grid=c(0.2,0.2),
  grid.col=c("blue","yellow")
)
```

## Cross Validation Cubic SVM
```{r}
library(e1071)

set.seed(123) # Set seed for reproducibility

# Combine X and y into a single dataframe
data <- cbind(X, y)

# Perform 5-fold cross-validation
num_folds <- 5
folds <- cut(seq(1, nrow(data)), breaks = num_folds, labels = FALSE)

# Create empty vectors to store the predictions and actual values
all_predictions <- vector()
all_actuals <- vector()

for (i in 1:num_folds) {
  # Split the data into training and test sets for the current fold
  train_data <- data[folds != i, ]
  test_data <- data[folds == i, ]
  
  # Train the Cubic SVM model
  cubic_svm_model <- svm(dod ~ ., data = train_data, kernel = "polynomial", degree = 3)
  
  # Make predictions on the test set
  predictions <- predict(cubic_svm_model, newdata = test_data)
  
  # Append the predictions and actual values to the vectors
  all_predictions <- c(all_predictions, predictions)
  all_actuals <- c(all_actuals, test_data$dod)
}

# Calculate performance metrics on the entire dataset
confusion_matrix <- table(all_actuals, all_predictions)

## Calculate Accuracy
accuracy <- sum(diag(confusion_matrix)) / sum(confusion_matrix)
cat("Accuracy:", accuracy, "\n")

## Calculate Recall
recall <- diag(confusion_matrix)[1] / sum(confusion_matrix[1,])
cat("Recall:", recall, "\n")

## Calculate F1 Score
precision <- diag(confusion_matrix)[1] / colSums(confusion_matrix)[1]
f1_score <- 2 * (precision * recall) / (precision + recall)
cat("F1 Score:", f1_score, "\n")
```

## Cross Validation Cubic SVM

```{r}
library(pROC)

# Calculate ROC curve using the actual values and predictions
roc_obj <- roc(all_actuals, all_predictions)

# Plot the ROC curve
plot(
  roc_obj,
  col = "blue",
  main = "ROC Curve - Cubic SVM (Cross-Validation)",
  legacy.axes = TRUE,
  print.auc = TRUE,
  grid = c(0.2, 0.2),
  grid.col = c("green", "orange")
)