---
title: "LR"
output: 
  html_notebook: 
    toc: true
    theme: cosmo
---

# Setting

```{r}
rm(list=ls(all=TRUE))
setwd('C:/Users/sitdo/Documents/GitHub/IBD-EDA/aes/')
```

# Loading Data

```{r}
library(dplyr)

data <- read.csv("./data_processed/data_die_in_icu_with_commorbidities.csv") %>% select(-1)

data$los <- if_else(data$los <= 4, 0, 1)
```


# Installing Packages

```{r}
library(MASS)
library(caret)
```

# Without Selection

Building Formula

```{r}
variables <- setdiff(names(data), "los")

variables_str <- paste(variables, collapse = " + ")
formula_str <- paste("los ~", variables_str)

formula <- as.formula(formula_str)
```

## Method I: Splitting Data

```{r}
set.seed(123)
splitting_ratio <- 0.7

indices <- 1:nrow(data)
shuffled_indices <- sample(indices) 
train_size <- floor(splitting_ratio * length(indices))

train_indices <- shuffled_indices[1:train_size]
test_indices <- shuffled_indices[(train_size + 1):length(indices)]

train_data <- data[train_indices, ]
test_data <- data[test_indices, ]
```



```{r}
model <- glm(formula = formula, 
             family = binomial, 
             data = train_data)

summary_model <- summary(model)
print(summary_model)
```

### Performance

```{r}
predictions <- predict(model, test_data, type="response")
```

#### Confusion Matrix

```{r}
confusion_matrix <- table(
  as.numeric(test_data$los), as.numeric(ifelse(predictions > 0.5, 1, 0))
)

TP <- confusion_matrix[1, 1]
TN <- confusion_matrix[2, 2]
FP <- confusion_matrix[2, 1]
FN <- confusion_matrix[1, 2]

## Calculate Accuracy
accuracy <- (TP + TN) / (TP + FP + TN + FN)
cat("Accuracy:", accuracy, "\n")

## Calculate Recall
recall <- TP / (TP + FN)
cat("Recall:", recall, "\n")

## Calculate Precision
precision <- TP / (TP + FP)
cat("Precision:", precision, "\n")

## Calculate Specificity
specificity <- TN / (TN + FP)
cat("Specificity:", specificity, "\n")

## Calculate F1 Score
f1_score <- 2 * (precision * recall) / (precision + recall)
cat("F1 Score:", f1_score, "\n")
```

#### ROC Curve

```{r}
library(pROC)
# Calculate ROC curve using the actual values and predictions
roc_obj <- roc(
  as.numeric(test_data$los), predictions
)

# Plot the ROC curve
plot(
  roc_obj,
  col = "blue",
  main = "ROC Curve - Logistic Regression",
  legacy.axes = TRUE,
  print.auc = TRUE,
  print.thres = TRUE,
  grid = c(0.2, 0.2),
  grid.col = c("green", "orange")
)
```

## Method II: Cross Validation

```{r}
# Perform 10-fold cross-validation
num_folds <- 10

folds <- cut(seq(1, nrow(data)), breaks = num_folds, labels = FALSE)

# Create empty vectors to store the predictions and actual values
all_predictions <- vector()
all_actuals <- vector()

for (i in 1:num_folds) {
  # Split the data into training and test sets for the current fold
  train_data <- data[folds != i, ]
  test_data <- data[folds == i, ]
  
  # Logistic Regression
  model <- glm(formula = formula, family = binomial, data = train_data)

  predictions <- predict(model, test_data, type="response")

  # Append the predictions and actual values to the vectors
  all_predictions <- c(all_predictions, predictions)
  all_actuals <- c(all_actuals, test_data$los)
}

```

### Performance

#### Confusion Matrix

```{r}
confusion_matrix <- table(
  as.numeric(all_actuals), as.numeric(ifelse(all_predictions > 0.5, 1, 0))
)

TP <- confusion_matrix[1, 1]
TN <- confusion_matrix[2, 2]
FP <- confusion_matrix[2, 1]
FN <- confusion_matrix[1, 2]

## Calculate Accuracy
accuracy <- (TP + TN) / (TP + FP + TN + FN)
cat("Accuracy:", accuracy, "\n")

## Calculate Recall
recall <- TP / (TP + FN)
cat("Recall:", recall, "\n")

## Calculate Precision
precision <- TP / (TP + FP)
cat("Precision:", precision, "\n")

## Calculate Specificity
specificity <- TN / (TN + FP)
cat("Specificity:", specificity, "\n")

## Calculate F1 Score
f1_score <- 2 * (precision * recall) / (precision + recall)
cat("F1 Score:", f1_score, "\n")
```

#### ROC Curve

```{r}
# Calculate ROC curve using the actual values and predictions
roc_obj <- roc(
  as.numeric(all_actuals), all_predictions
)

# Plot the ROC curve
plot(
  roc_obj,
  col = "blue",
  main = "ROC Curve - Logistic Regression (Cross Validation)",
  legacy.axes = TRUE,
  print.auc = TRUE,
  print.thres = TRUE,
  grid = c(0.2, 0.2),
  grid.col = c("green", "orange")
)
```

# With Selecting

## Method I: Splitting Data

```{r}
splitting_ratio <- 0.7

indices <- 1:nrow(data)
shuffled_indices <- sample(indices) 
train_size <- floor(splitting_ratio * length(indices))

train_indices <- shuffled_indices[1:train_size]
test_indices <- shuffled_indices[(train_size + 1):length(indices)]

train_data <- data[train_indices, ]
test_data <- data[test_indices, ]
```

Building Formula

```{r}
removed_variables <- c("")

variables <- setdiff(names(data), c("los", removed_variables))

formula_str <- paste("los ~", paste(variables, collapse = " + "))

new_formula <- as.formula(formula_str)
```

AIC Step

```{r}
p_value_threshold <- 0.1

repeat {
  new_model <- glm(
    formula = new_formula,
    family = binomial,
    data = train_data
  )
  
  summary_model <- summary(new_model)

  p_values <- summary_model$coefficients[, "Pr(>|z|)"]
  
  max_p_value <- max(p_values)
  max_p_value_attribute <- names(which.max(p_values))
  
  # 检查最大P值是否超过阈值
  if (max_p_value > p_value_threshold) {
      # 如果超过阈值，从公式中移除该变量并继续循环
      print(max_p_value_attribute)
    
      removed_variables <- c(removed_variables, max_p_value_attribute)
      
      variables <- setdiff(names(train_data), c("los", removed_variables))
      
      formula_str <- paste("los ~", paste(variables, collapse = " + "))
      
      new_formula <- as.formula(formula_str)
  } else {
      # 如果所有变量的P值都不超过阈值，则停止循环
      break
  }
}

```

## Final Model

```{r}
print(new_formula)
```

```{r}
final_model <- glm(
  formula = new_formula,
  family = binomial,
  data = train_data
)

summary_model <- summary(final_model)
print(summary_model)
```

### Performance

```{r}
predictions <- predict(final_model, test_data, type="response")
```

#### Confusion Matrix

```{r}
confusion_matrix <- table(
  as.numeric(test_data$los), as.numeric(ifelse(predictions > 0.5, 1, 0))
)

TP <- confusion_matrix[1, 1]
TN <- confusion_matrix[2, 2]
FP <- confusion_matrix[2, 1]
FN <- confusion_matrix[1, 2]

## Calculate Accuracy
accuracy <- (TP + TN) / (TP + FP + TN + FN)
cat("Accuracy:", accuracy, "\n")

## Calculate Recall
recall <- TP / (TP + FN)
cat("Recall:", recall, "\n")

## Calculate Precision
precision <- TP / (TP + FP)
cat("Precision:", precision, "\n")

## Calculate Specificity
specificity <- TN / (TN + FP)
cat("Specificity:", specificity, "\n")

## Calculate F1 Score
f1_score <- 2 * (precision * recall) / (precision + recall)
cat("F1 Score:", f1_score, "\n")
```

#### ROC Curve

```{r}
library(pROC)
# Calculate ROC curve using the actual values and predictions
roc_obj <- roc(
  as.numeric(test_data$los), predictions
)

# Plot the ROC curve
plot(
  roc_obj,
  col = "blue",
  main = "ROC Curve - Logistic Regression",
  legacy.axes = TRUE,
  print.auc = TRUE,
  print.thres = TRUE,
  grid = c(0.2, 0.2),
  grid.col = c("green", "orange")
)
```

#### CI

```{r}
ci <- confint(final_model)
exp(cbind(OR <- coef(final_model), ci))
```

## Method II: Cross Validation

```{r}
# Perform 10-fold cross-validation
num_folds <- 10

folds <- cut(seq(1, nrow(data)), breaks = num_folds, labels = FALSE)
```

```{r}
# Create empty vectors to store the predictions and actual values
all_predictions <- vector()
all_actuals <- vector()

for (i in 1:num_folds) {
  # Split the data into training and test sets for the current fold
  train_data <- data[folds != i, ]
  test_data <- data[folds == i, ]
  
  # Logistic Regression
  model <- glm(formula = new_formula, 
               family = binomial, 
               data = train_data)

  predictions <- predict(model, test_data, type="response")

  # Append the predictions and actual values to the vectors
  all_predictions <- c(all_predictions, predictions)
  all_actuals <- c(all_actuals, test_data$los)
}
```

### Performance

#### Confusion Matrix

```{r}
confusion_matrix <- table(
  as.numeric(all_actuals), as.numeric(ifelse(all_predictions > 0.5, 1, 0))
)

TP <- confusion_matrix[1, 1]
TN <- confusion_matrix[2, 2]
FP <- confusion_matrix[2, 1]
FN <- confusion_matrix[1, 2]

## Calculate Accuracy
accuracy <- (TP + TN) / (TP + FP + TN + FN)
cat("Accuracy:", accuracy, "\n")

## Calculate Recall
recall <- TP / (TP + FN)
cat("Recall:", recall, "\n")

## Calculate Precision
precision <- TP / (TP + FP)
cat("Precision:", precision, "\n")

## Calculate Specificity
specificity <- TN / (TN + FP)
cat("Specificity:", specificity, "\n")

## Calculate F1 Score
f1_score <- 2 * (precision * recall) / (precision + recall)
cat("F1 Score:", f1_score, "\n")
```

#### ROC Curve

```{r}
# Calculate ROC curve using the actual values and predictions
roc_obj <- roc(
  as.numeric(all_actuals), all_predictions
)

# Plot the ROC curve
plot(
  roc_obj,
  col = "blue",
  main = "ROC Curve - Logistic Regression (Cross Validation)",
  legacy.axes = TRUE,
  print.auc = TRUE,
  print.thres = TRUE,
  grid = c(0.2, 0.2),
  grid.col = c("green", "orange")
)
```
